The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-21 project/paper/output.tex
Tweaked intro to properties section.

The skew-normal distribution is similar to the normal but with an added
parameter for skew, allowing it to lean asymmetrically to the left or right. In
this section, we'll acquaint ourselves with some of its basic properties.

>>>>

The skew-normal distribution is similar to the normal but with an added
parameter for skew that allows it to lean to the left or right. In this
section, we'll get to know some of its basic properties.

### 2011-01-21 project/paper/properties.tex
Reworked intro (added labels to other sections, renamed one)
Tweaked intro to properties section.

\section{The Skew-Normal}

The skew-normal distribution is similar to the normal but with an added
parameter for skew, allowing it to lean asymmetrically to the left or right. In
this section, we'll acquaint ourselves with some of its basic properties.

>>>>

\section{The Skew-Normal}
\label{sec:properties}

The skew-normal distribution is similar to the normal but with an added
parameter for skew that allows it to lean to the left or right. In this
section, we'll get to know some of its basic properties.
